\vspace{-2cm} Inference on the Effects of Observed Features \\ in Latent Space Models for Networks

### 2016-09-07 manuscript.tex
update to iterations line

The LSM is estimated using the canonical implementation in the \texttt{latentnet} package in \texttt{R} \citep{latentnet}. For each iteration of the simulation, we run 10,000 burn in iterations, followed by 1,000,000 iterations of the sampler. Every 100th post burn in iteration is saved. Convergence in the log probability of the model is assessed using the Geweke diagnostic in the \texttt{coda} package \citep{coda, geweke1991evaluating}. If the convergence criterion is satisfied, the simulation continues to the next set of arguments, otherwise the number of iterations is doubled. If the convergence criterion is still not satisfied, then the aforementioned step in the simulation is flagged for review [ZACH, would you elaborate on this..what did we do with these iterations, and how often did this happen]. At each point in the simulation's parameter space, we execute 1,000 Monte Carlo iterations. \footnote{One of the primary difficulties in executing the above simulation design is the computational cost of estimating the LSM. We utilize the \texttt{BatchExperiments} \R package to construct and execute our computational experiments on a Torque cluster \cite{bischl2015batchjobs}.}

>>>>

The LSM is estimated using the canonical implementation in the \texttt{latentnet} package in \texttt{R} \citep{latentnet}. For each iteration of the simulation, we run 10,000 burn in iterations, followed by 1,000,000 iterations of the sampler. Every 100th post burn in iteration is saved. Convergence in the log probability of the model is assessed using the Geweke diagnostic in the \texttt{coda} package \citep{coda, geweke1991evaluating}. If the convergence criterion is satisfied, the simulation continues to the next set of arguments, otherwise the number of iterations is doubled. If the convergence criterion is still not satisfied, then the aforementioned step in the simulation is flagged for review. However, this was not necessary in any cases. At each point in the simulation's parameter space, we execute 1,000 Monte Carlo iterations. \footnote{One of the primary difficulties in executing the above simulation design is the computational cost of estimating the LSM. We utilize the \texttt{BatchExperiments} \R package to construct and execute our computational experiments on a Torque cluster \cite{bischl2015batchjobs}.}
